---
title: "Trait exploration"
author: "Mark Miller"
date: "2 October 2018"
output: html_document
runtime: shiny
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```



```{r}
# 20/09/2018

# Initial explore of fish and coral survey and trait data

library(dplyr)
library(readxl)
library(ggplot2)
library(reshape2)
library(gridExtra)
#https://daijiang.name/en/2014/05/11/functional-diversity-in-r/
library(FD)
library(ade4)
library(cluster)
library(factoextra)
library(Rtsne)
library(rmdexamples)

#setwd("~/leeds_postdoc")
setwd("M:/coral_fish")


# read in coral and fish abundance and trait data

fishdat<-read_excel('data/RMI/RMIfish_siteDepthMeans_ADepth.xlsx', sheet=1)

fishtrait<-read.csv('data/Traits/RMI_fish_traits4.csv', h=T)

#test names line up

n1<-names(fishdat)[-1] # without site col name
n2<-fishtrait$Species

# FYI more species in trait dataset than abundance dataset

ingrid<-expand.grid(n1, n2)
ingrid$Var1<-as.character(ingrid$Var1)
ingrid$Var2<-as.character(ingrid$Var2)

ingrid$test=ingrid$Var1==ingrid$Var2

ingrid_out<- ingrid %>% group_by(Var1) %>%
  summarise(has_trait=TRUE%in%test)

#filter(ingrid_out, has_trait==F)
# only Bryanops natans
# called Bryaninops natans in trait data - correct
names(fishdat)[names(fishdat)=='Bryanops natans']<-'Bryaninops natans'

# Now for coral data

# read in coral and fish abundance and trait data

coraldat<-read.csv('data/RMI/RMI_corals_A.csv', h=T)

coraltrait<-read.csv('data/Traits/RMI_coralTraits4May15.csv', h=T)

# replace '.' between family & species name in abundance data
names(coraldat)<-gsub('\\.', '\\ ', names(coraldat))

#test names line up

n1<-names(coraldat)[-1] # without site col name
n2<-coraltrait$Species

# FYI more species in trait dataset than abundance dataset

ingrid<-expand.grid(n1, n2)
ingrid$Var1<-as.character(ingrid$Var1)
ingrid$Var2<-as.character(ingrid$Var2)

ingrid$test=ingrid$Var1==ingrid$Var2

ingrid_out<- ingrid %>% group_by(Var1) %>%
  summarise(has_trait=TRUE%in%test)

#filter(ingrid_out, has_trait==F)
# two 'sp.' species had the '.' removed by gsub above
names(coraldat)[names(coraldat)=='Acropora sp ']<-'Acropora sp.'
names(coraldat)[names(coraldat)=='Alveopora sp ']<-'Alveopora sp.'

# prepare trait data for Gower distance calculation

# filter to only include traits that are in abundance data

fishtrait2<-filter(fishtrait, Species%in% names(fishdat))

row.names(fishtrait2)<-fishtrait2$Species

# drop trait 'PD50' as seems to cock up calculaion
fishtrait2<-fishtrait2[,c(3:5,7:length(fishtrait2))]
# could also drop 'Function' as coarse representative of 'Food'?


##~~~~~~~~~~~~ Trial using FD package ~~~~~~~~~~~##

#get abundance data into matrix and remove site and region variables

fish_matx<-as.matrix(data.frame(fishdat[,2:371]))

dimnames(fish_matx)[[1]]<-fishdat$X__1
dimnames(fish_matx)[[2]]<-names(fishdat)[2:371]

# run checks for FD
# abun values > 0
#which(colSums(fish_matx, na.rm=T)==0)# none
#which(colSums(fish_matx, na.rm=T)<2)# fair few

# check levels and see if any are unbalanced

#str(fishtrait2)

# run with different traits and see which cause issues
temp<-functcomp(fishtrait2[,c(1:4, 6:7)], fish_matx)
# bad columns: 5,8,9,11

#table(fishtrait2$Food)
#table(fishtrait2$Position)
#table(fishtrait2$SpawnMode)
#table(fishtrait2$Active)

# the subsetting has left factors with 0s, fix

fishtrait2$Food<-factor(fishtrait2$Food)
fishtrait2$Position<-factor(fishtrait2$Position)
fishtrait2$SpawnMode<-factor(fishtrait2$SpawnMode)
fishtrait2$Active<-factor(fishtrait2$Active)

funct_comp<-functcomp(fishtrait2, fish_matx, CWM.type = c("dom", "all"), bin.num = NULL) #doesn't work unless it's a matrix?
# ok fixed

# run fd

fishtrait_dist<-gowdis(fishtrait2)

funct_disp<-fdisp(fishtrait_dist, fish_matx)

funct_comp<-functcomp(fishtrait2, fish_matx, CWM.type = c("dom", "all"), bin.num = NULL) #doesn't work unless it's a matrix?

FDdata<-dbFD(fishtrait2, fish_matx, corr='cailliez', calc.FRic=F, print.pco=T, messages=F)


#getting out of DB
FRic<-FDdata$FRic 
nbsp<-FDdata$nbsp
sing.sp<-FDdata$sing.sp
FEve<-FDdata$FEve
FDis<-FDdata$FDis
RaoQ<-FDdata$RaoQ

funcDF<-data.frame(sing.sp, FEve, FDis, RaoQ)

```

# Plotting trait space

### Construct PCoA plot of trait space and see where different families sit

```{r}

##~~~~~~~~~~~~ Plotting trait space ~~~~~~~~~~~##
## e.g. Mouillot et al (2014) and Mcwilliam (2018)

#is.euclid(fishtrait_dist) # not euclidean so needs transforming for use in pcoa

fishtrait_dist2 <- cailliez(fishtrait_dist)

pc1<-pcoa(fishtrait_dist2)

pc2<-dudi.pco(d = fishtrait_dist2, scannf = FALSE, nf = 4)

#screeplot(pc2)
#biplot(pc2) # yikes

#https://www.r-bloggers.com/7-functions-to-do-metric-multidimensional-scaling-in-r/
ppp <- ggplot() + coord_fixed() + 
  labs(x="PCoA1", y="PCoA2") +
  geom_hline(yintercept=0, col="darkgrey") + 
  geom_vline(xintercept=0, col="darkgrey")


pc2.dfs <- data.frame(pc2$li, fishtrait2)
pc2.dfs$Species<-row.names(pc2.dfs)
pc2.dfs<-left_join(pc2.dfs, fishtrait[,1:2], by='Species')

#plot gloab trait space by family
ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=Family))
```

### Use trait space to visualise gradients within traits

```{r,  fig.height=16, fig.width=8}
# and for each trait
p1<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=HomeRange))+scale_colour_gradientn(colors=topo.colors(10))
p2<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=MaxLength))+scale_colour_gradientn(colors=topo.colors(10))
p3<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=PLD_Mean))+scale_colour_gradientn(colors=topo.colors(10))
p4<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=TrophLevel))+scale_colour_gradientn(colors=topo.colors(10))

p5<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=Food))
p6<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=Function))
p7<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=Aggregation))
p8<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=Position))
p9<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=SpawnMode))
p10<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=ParentalMode))
p11<-ppp + geom_point(data=pc2.dfs, aes(x=A1, y=A2, colour=Active))

# plot easily visualised traits together
grid.arrange(p2,p4,p6,p7,p8,p9,p10,p11, ncol=2)
```

### Summarise where each regional fish community sits within global (all regions) trait space

```{r}
# attribute PCOA species with counts per RMI region
fishdat$region=substr(fishdat$X__1, 1,2)

reg_count<-fishdat[,-1]%>%group_by(region)%>%
  summarise_all(sum, na.rm=T)

reg_count2<-data.frame(t(data.frame(reg_count)[,-1]))

names(reg_count2)<-c('Ailuk', 'Majuro', 'Rongerik', 'Rongelap')
reg_count2$Species<-names(fishdat)[2:371]
row.names(reg_count2)<-reg_count2$Species

pc2.dfs<-left_join(pc2.dfs, reg_count2, by='Species')

#subset for regional points with > 0 fish species
ailuk_df<-pc2.dfs[pc2.dfs$Ailuk>0,]
majuro_df<-pc2.dfs[pc2.dfs$Majuro>0,]
rongerik_df<-pc2.dfs[pc2.dfs$Rongerik>0,]
rongelap_df<-pc2.dfs[pc2.dfs$Rongelap>0,]

#hulls
glob_hull<-pc2.dfs[chull(pc2.dfs$A1, pc2.dfs$A2),]

ailuk_hull<-ailuk_df[chull(ailuk_df$A1, ailuk_df$A2),]
majuro_hull<-majuro_df[chull(majuro_df$A1, majuro_df$A2),]
rongerik_hull<-rongerik_df[chull(rongerik_df$A1, rongerik_df$A2),]
rongelap_hull<-rongelap_df[chull(rongelap_df$A1, rongelap_df$A2),]

p1<-ppp+
  geom_polygon(data=glob_hull,aes(x=A1,y=A2),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A1, y=A2), colour='grey70')+theme_bw()+
  geom_polygon(data=ailuk_hull,aes(x=A1,y=A2),alpha=0.09, fill='red',colour="black")+
  geom_point(data=ailuk_df, aes(x=A1, y=A2), colour='red')+theme_bw()+labs(title='Ailuk')

p2<-ppp+
  geom_polygon(data=glob_hull,aes(x=A1,y=A2),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A1, y=A2), colour='grey70')+theme_bw()+
  geom_polygon(data=majuro_hull,aes(x=A1,y=A2),alpha=0.09, fill='green',colour="black")+
  geom_point(data=majuro_df, aes(x=A1, y=A2), colour='green')+theme_bw()+labs(title='Majuro')


p3<-ppp+
  geom_polygon(data=glob_hull,aes(x=A1,y=A2),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A1, y=A2), colour='grey70')+theme_bw()+
  geom_polygon(data=rongerik_hull,aes(x=A1,y=A2),alpha=0.09, fill='blue',colour="black")+
  geom_point(data=rongerik_df, aes(x=A1, y=A2), colour='blue')+theme_bw()+labs(title='Rongerik')


p4<-ppp+
  geom_polygon(data=glob_hull,aes(x=A1,y=A2),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A1, y=A2), colour='grey70')+theme_bw()+
  geom_polygon(data=rongelap_hull,aes(x=A1,y=A2),alpha=0.09, fill='purple',colour="black")+
  geom_point(data=rongelap_df, aes(x=A1, y=A2), colour='purple')+theme_bw()+labs(title='Rongelap')

grid.arrange(p1, p2, p3, p4, ncol=2)


```

### And same plot for PCoA Axis 3 & 4

```{r}

ppp <- ggplot() + coord_fixed() + 
  labs(x="PCoA3", y="PCoA4") +
  geom_hline(yintercept=0, col="darkgrey") + 
  geom_vline(xintercept=0, col="darkgrey")

ailuk_df<-pc2.dfs[pc2.dfs$Ailuk>0,]
majuro_df<-pc2.dfs[pc2.dfs$Majuro>0,]
rongerik_df<-pc2.dfs[pc2.dfs$Rongerik>0,]
rongelap_df<-pc2.dfs[pc2.dfs$Rongelap>0,]

#hulls
glob_hull<-pc2.dfs[chull(pc2.dfs$A3, pc2.dfs$A4),]

ailuk_hull<-ailuk_df[chull(ailuk_df$A3, ailuk_df$A4),]
majuro_hull<-majuro_df[chull(majuro_df$A3, majuro_df$A4),]
rongerik_hull<-rongerik_df[chull(rongerik_df$A3, rongerik_df$A4),]
rongelap_hull<-rongelap_df[chull(rongelap_df$A3, rongelap_df$A4),]

p1<-ppp+
  geom_polygon(data=glob_hull,aes(x=A3,y=A4),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A3, y=A4), colour='grey70')+theme_bw()+
  geom_polygon(data=ailuk_hull,aes(x=A3,y=A4),alpha=0.09, fill='red',colour="black")+
  geom_point(data=ailuk_df, aes(x=A3, y=A4), colour='red')+theme_bw()+labs(title='Ailuk')

p2<-ppp+
  geom_polygon(data=glob_hull,aes(x=A3,y=A4),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A3, y=A4), colour='grey70')+theme_bw()+
  geom_polygon(data=majuro_hull,aes(x=A3,y=A4),alpha=0.09, fill='green',colour="black")+
  geom_point(data=majuro_df, aes(x=A3, y=A4), colour='green')+theme_bw()+labs(title='Majuro')


p3<-ppp+
  geom_polygon(data=glob_hull,aes(x=A3,y=A4),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A3, y=A4), colour='grey70')+theme_bw()+
  geom_polygon(data=rongerik_hull,aes(x=A3,y=A4),alpha=0.09, fill='blue',colour="black")+
  geom_point(data=rongerik_df, aes(x=A3, y=A4), colour='blue')+theme_bw()+labs(title='Rongerik')


p4<-ppp+
  geom_polygon(data=glob_hull,aes(x=A3,y=A4),fill=NA,colour="grey70")+
  geom_point(data=pc2.dfs, aes(x=A3, y=A4), colour='grey70')+theme_bw()+
  geom_polygon(data=rongelap_hull,aes(x=A3,y=A4),alpha=0.09, fill='purple',colour="black")+
  geom_point(data=rongelap_df, aes(x=A3, y=A4), colour='purple')+theme_bw()+labs(title='Rongelap')

grid.arrange(p1, p2, p3, p4, ncol=2)

```

# Clustering

Lets try some cluster analyses on the trait data to try and pull outdifferent functional groups, first up hierarchical partitioning.*using a set number of groups (k=8)*

```{r, fig.height=12, fig.width=12}

##~~~~~~~~~~~~ clustering trials ~~~~~~~~~~~##

## hierarchical clustering

FDis_clust = hclust (fishtrait_dist, method = "ward.D") 


# plot(FDis_clust, labels = fish.traits$Species, cex = 0.1)
### display as ring
FDisClus_phy = as.phylo(FDis_clust)
labelClust = as.character (row.names(fishtrait2))
FDisClus_phy$tip.label = labelClust
colours=rainbow(8)
clus6<-cutree(FDis_clust, k=8)

plot(FDisClus_phy, type="fan", use.edge.length = TRUE, node.pos = NULL,
     show.tip.label = TRUE, show.node.label = FALSE, tip.color = colours[clus6] ,
     edge.width = 1, edge.lty = 1, font = 2, cex = 0.5, label.offset = 0.1)
```

Now trial using Partitioning Around Mediods (PAM) clustering,
which is similar to K-means but less sensistive to outliers and 
more appropriate for categorical data

First have a look at correlation between species, based on correlation of Gower trait distance

```{r, fig.cap= '1 = perfect difference, 0 = identical'  }

### Kmeans and Partitioning Around Mediods (PAM)
# https://www.r-bloggers.com/clustering-mixed-data-types-in-r/
# http://www.sthda.com/english/articles/27-partitioning-clustering-essentials/88-k-medoids-essentials/
# https://lukedaniels1.github.io/Bio381_2018/Daniels_Cluster_Analysis_Lecture.html

# Have a look in factoextra package

DistanceMap <- fviz_dist(fishtrait_dist, order = TRUE, show_labels = TRUE, lab_size = 4)

DistanceMap
# 0 means identical gower distance
```

We can use the check the Gower distances are correct but ouputting the most similar species pair.. 

```{r}

gower_mat <- as.matrix(fishtrait_dist)

# Output most similar pair

fishtrait2[
  which(gower_mat == min(gower_mat[gower_mat != min(gower_mat)]),
        arr.ind = TRUE)[1, ], ]
```

And the most dissimilar species pair 

```{r}

# and least similar
fishtrait2[
  which(gower_mat == max(gower_mat[gower_mat != min(gower_mat)]),
        arr.ind = TRUE)[1, ], ]
```

Need to decide the optimum number of clusters. We calculate the silhouette width, looking for the highest value (from reasonably low number of clusters) - 8 looks good

```{r}

# Calculate silhouette width for many k using PAM

sil_width <- c(NA)

for(i in 2:20){
  
  pam_fit <- pam(fishtrait_dist,diss = TRUE, k = i)
  
  sil_width[i] <- pam_fit$silinfo$avg.width
  
}

# Plot sihouette width (higher is better)

qplot(x=1:20, y=sil_width)+labs(x="Number of clusters", y= "Silhouette Width")+
 geom_line() +scale_x_continuous(breaks=2:20)
# fyi keeps going upn after 12... 8 clusters looks good
```

We fit PAM clustering model with 8 clusters and can then view the summary of traits within each cluster

```{r}

## We can see the summary values for traits within each cluster

pam1<- pam(fishtrait_dist,diss = TRUE, k = 8)

pam_results <- fishtrait2 %>%
  mutate(cluster = pam1$clustering) %>%
  group_by(cluster) %>%
  do(the_summary = summary(.))

pam_results$the_summary

```

We can also see the mediod of each cluster, which is the exemplar species from each cluster

```{r}

## We can also see the mediod of each cluster, which is the
## exemplar species from each cluster

fishtrait2_cl<-fishtrait2
fishtrait2_cl$cluster<-pam1$clustering

fishtrait2_cl[pam1$medoids,]

```

And now we can visualise how each cluster is represented by the different trait values

```{r}

# make plots 


p<-ggplot(data=fishtrait2_cl, aes(x=factor(cluster)))+labs(x='Cluster')

p1<-p+geom_boxplot(aes(y=HomeRange))+ylim(c(0,10))
p2<-p+geom_boxplot(aes(y=MaxLength))+ylim(c(0,100))
p3<-p+geom_boxplot(aes(y=PLD_Mean))+ylim(c(0,100))
p4<-p+geom_boxplot(aes(y=TrophLevel))

# bit different for  categorialc variables

p5<-ggplot(data=fishtrait2_cl %>% group_by(cluster,Food) %>% 
  summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
  aes(x=factor(cluster), y=perc, fill=Food))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "Food")+theme_bw()

p6<-ggplot(data=fishtrait2_cl %>% group_by(cluster,Function) %>% 
             summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
           aes(x=factor(cluster), y=perc, fill=Function))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "Function")+theme_bw()

p7<-ggplot(data=fishtrait2_cl %>% group_by(cluster,Aggregation) %>% 
             summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
           aes(x=factor(cluster), y=perc, fill=Aggregation))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "Aggregation")+theme_bw()

p8<-ggplot(data=fishtrait2_cl %>% group_by(cluster,Position) %>% 
             summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
           aes(x=factor(cluster), y=perc, fill=Position))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "Position")+theme_bw()

p9<-ggplot(data=fishtrait2_cl %>% group_by(cluster,Position) %>% 
             summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
           aes(x=factor(cluster), y=perc, fill=Position))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "Position")+theme_bw()

p10<-ggplot(data=fishtrait2_cl %>% group_by(cluster,SpawnMode) %>% 
             summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
           aes(x=factor(cluster), y=perc, fill=SpawnMode))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "SpawnMode")+theme_bw()

p11<-ggplot(data=fishtrait2_cl %>% group_by(cluster,ParentalMode) %>% 
             summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
           aes(x=factor(cluster), y=perc, fill=ParentalMode))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "ParentalMode")+theme_bw()

p12<-ggplot(data=fishtrait2_cl %>% group_by(cluster,Active) %>% 
              summarise(count=n()) %>% mutate(perc=(count/sum(count))*100), 
            aes(x=factor(cluster), y=perc, fill=Active))+
  geom_bar(stat="identity", width = 0.7) +
  labs(x = "Cluster", y = "Percent", fill = "Active")+theme_bw()


p1; p2; p3; p4;p5; p6; p7; p8; p9; p10; p11; p12
```

# View clusters in reduced-axes space

We can now try to visualise the clusters in multidensional space. First try a couple of PCA visualisations - tricky because of lots of data

```{r}

# Now we can visualise using pca, sort of..

fviz_cluster(object=list(data=fishtrait_dist, cluster = pam1$clustering), 
            ellipse.type = "t", # Concentration ellipse
            repel = TRUE, # Avoid label overplotting (slow)
            ggtheme = theme_classic())

fviz_cluster(object=list(data=fishtrait_dist, cluster = pam1$clustering), 
             ellipse.type = "t", # Concentration ellipse
             repel = F, 
             geom='point',ggtheme = theme_classic())

fviz_cluster(object=list(data=fishtrait_dist, cluster = pam1$clustering), 
             ellipse=F,
             repel = F,
             shape=1,
             geom='point',ggtheme = theme_classic())
```

We can also visualise using Rtsne (Barnes-Hut implementation of t-Distributed Stochastic Neighbor Embedding) *I have no idea how this MDS scaling method works, just for visualising really*

```{r}

## Alternative visualisation using Rtsne

tsne_obj <- Rtsne(fishtrait_dist, is_distance = TRUE)

tsne_data <- tsne_obj$Y %>%
    data.frame() %>%
     setNames(c("X", "Y")) %>%
     mutate(cluster = factor(pam1$clustering),
    name = row.names(fishtrait2))

   ggplot(aes(x = X, y = Y), data = tsne_data) +
   geom_point(aes(color = cluster))+theme_bw()
```

Fianlly, we can validate our identified clusters using silhoette metric. The closer the value to 1, the more likely the observation is to be in correct cluster, close to 0 means observation lies between clusters and negative values mean the observation is liekly in the wrong cluster - on this basis some of our clusters don't look great. 

```{r}
# we can validate with silhoette

fviz_silhouette(silhouette(pam1))

# The closer the value to 1, the more likely the observation is to be in correct cluster, 
# close to 0 means observation lies between clusters and negative values
# mean the observation is liekly in the wrong cluster.

```


Have a look interactively with PAM clustering


```{r}
 vars = names(fishtrait2)

  shinyApp(
    ui = fluidPage(
      fluidRow(style = "padding-bottom: 20px;",
        column(4, numericInput('clusters', 'Cluster count', 3,
                               min = 1, max = 9))
      ),
      fluidRow(
        plotOutput('kmeans', height = "400px")
      )
    ),

    server = function(input, output, session) {
      
      
    

      # Combine the selected variables into a new data frame
   

      clusters = reactive({
        pam(fishtrait_dist,diss = TRUE, k = input$clusters)
      })
      


      
         selectedData = reactive({
        tsne_obj$Y %>%
    data.frame() %>%
     setNames(c("X", "Y")) %>% `rownames<-` (row.names(fishtrait2))
      })

      output$kmeans = renderPlot(height = 400, {
        res = clusters()
        par(mar = c(5.1, 4.1, 0, 1))
        plot(selectedData(),
             col = res$clustering, pch = 20, cex = 3)
        points(selectedData()[res$medoids,], pch = 4, cex = 4, lwd = 4)
      })
      
    
    },

    options = list(height = 500)
  )
```
